Transformation of forecasts for evaluating predictive performance in an epidemiological context

### 2023-01-12 main.tex

\title{Transformation of forecasts for evaluating predictive performance in an epidemiological context}
  \author{Nikos I. Bosse\thanks{Department of Infectious Disease Epidemiology, London School of Hygiene \& Tropical Medicine, London, United Kingdom} $^{,}$\thanks{Centre for the Mathematical Modelling of Infectious Diseases, London, United Kingdom} $^{,*}$, 
  Sam Abbott\footnotemark[1] $^{,}$\footnotemark[2]$ ^{}$, 
  Anne Cori\thanks{MRC Centre for Outbreak Analysis and Modelling, Department of Infectious Disease Epidemiology, School of Public Health, Imperial College London, London, United Kingdom} $^{}$, \\
  Edwin van Leeuwen\thanks{Department of Infectious Disease Epidemiology, London School of Hygiene \& Tropical Medicine, London, United Kingdom} $^{,}$\thanks{UK Health Security Agency, London, United Kingdom} $^{}$, 
  Johannes Bracher\thanks{Chair of Statistical Methods and Econometrics, Karlsruhe Institute of Technology, Karlsruhe, Germany} $^{}$, 
  Sebastian Funk\footnotemark[1] $^{,}$\footnotemark[2]$ ^{}$}

\maketitle
%\tableofcontents
\begin{abstract}
Forecast evaluation plays an essential role in improving forecasting models and can support their role in informing decision-making. In epidemiology, probabilistic forecasts are often scored using the Weighted Interval Score (WIS) or the Continuous Ranked Probability Score (CRPS), which are measures of absolute distance between forecast and observation. Infectious disease transmission is commonly modelled as an exponential process characterized by the growth rate or the effective reproduction number. However, if the true objective of the forecaster is to predict future growth rates or reproduction numbers then scoring based on the absolute distance between forecast and observation may not reflect this underlying task well and thus make it difficult to compare forecasts across time, space, and forecast targets. As a solution, we propose transforming the data before scoring the forecasts to better reflect the underlying generative process. We further propose the natural logarithm  as a candidate transformation and discuss its interpretation as a measure of relative error and as a score for an implicit forecast of the exponential growth rate. Applying the natural logarithm to data from the European COVID-19 Forecast Hub, we found that it changed model rankings, regardless of stratification by forecast date, location or target types, and emphasised situations in which models missed lower inflection points and consequent rises in numbers, while penalising missed peaks less severely. We conclude that appropriate transformations, of which the natural logarithm is only one possible option, should be considered when assessing the performance of different models in the context of infectious disease incidence. 
\end{abstract}

% Suggestion J:
% Forecast evaluation plays an essential role in the development cycle of predictive epidemic models and can inform their use for public health decision-making. Common scores to evaluate epidemiological forecasts are the Continuous Ranked Probability Score (CRPS) and the Weighted Interval Score (WIS), which are both measures of the absolute distance between the forecast distribution and the observation. They are commonly applied directly to predicted and observed incidence counts, but it can be questioned whether this yields the most meaningful results given the exponential nature of epidemic processes and the several orders of magnitude that observed values can span over space and time. In this paper, we argue that transforming counts before applying scores such as the CRPS or WIS can effectively mitigate these difficulties and yield epidemiologically meaningful and easily interpretable results. We motivate the procedure threefold using the CRPS on log-transformed counts as an example: firstly, it can be interpreted as a probabilistic version of a relative error. Secondly, it reflects how well models predicted the time-varying epidemic growth rate. And lastly, using arguments on variance-stabilizing transformations, it can be shown that under the assumption of a quadratic mean-variance relationship, the logarithmic transformation leads to expected CRPS values which are independent of the order of magnitude of the predicted quantity. This implies that different forecasting tasks will have a similar impact on overall evaluation results. Applying the log transformation to data and forecasts from the European COVID-19 Forecast Hub, we find that it changes model rankings regardless of stratification by forecast date, location or target types. Situations in which models missed beginning upward swings are more strongly emphasized while failing to predict a downturn following a peak is less severely penalized. We conclude that appropriate transformations, of which the natural logarithm is only one particularly attractive option, should be considered when assessing the performance of different models in the context of infectious disease incidence.

@@

The dynamics of infectious processes are often described by the complementary concepts of the reproduction number $R$ \citep{gosticPracticalConsiderationsMeasuring2020} and growth rate $r$ \citep{wallingaHowGenerationIntervals2007}, where $R$ describes the strength and $r$ the speed of epidemic growth \citep{dushoffSpeedStrengthEpidemic2021}.
In the absence of changes in immunity, behaviour or other factors that may affect the intensity of transmission, the reproduction number would be expected to remain approximately constant.
In that case, the number of new infections in the population grows exponentially in time.
This behaviour was observed, for example, early in the COVID-19 pandemic in many countries~\citep{pellisChallengesControlCOVID192021}.
If case numbers are evolving based on an exponential process and the  modelling task revolves around estimating the reproduction number or the corresponding growth rate, then evaluating forecasts based on the absolute distance between forecast and observed value penalises underprediction (of the reproduction number or growth rate) less than overprediction by the same amount. This is because errors on the observed value grow exponentially with the error on the estimated reproduction number or growth rate.
If one is to measure the ability of forecasts to assess and forecast the underlying infection dynamics, it may thus be more desirable to evaluate errors on the growth rate directly.

Evaluating forecasts using the CRPS or WIS means that scores represent a measure of absolute errors. However, forecast consumers may find errors on a relative scale easier to interpret and more useful in order to track predictive performance across targets of different orders of magnitude. 
\cite{bolinLocalScaleInvariance2021} have proposed the scaled CRPS (SCRPS) which is locally scale invariant; however, it does not correspond to a relative error measure and lacks a straightforward interpretation as available for the CRPS. % is less commonly used and does not have a straightforward equivalent for a setting with predictive quantiles. 
A closely related aspect to relative scores (as opposed to absolute scores) is that in the evaluation one may wish to give similar weight to all considered forecast targets. As the CRPS typically scales with the order of magnitude of the quantity to be predicted, this is not the case for the CRPS, which will typically assign higher scores to forecast targets with high expected values (e.g., in large locations or around the peak of an epidemic). \cite{bracherEvaluatingEpidemicForecasts2021} have argued that this is a desirable feature, directing attention to situations of particular public health relevance. An evaluation based on absolute errors, however, will assign little weight to other potentially important aspects, such as the ability to correctly predict future upswings while observed numbers are still low.

%that do not depend on the scale of the forecast target, such as the log score \citep{goodRationalDecisions1952}, which in addition is also invariant under monotonic transformations of the target, or a scaled version of the CRPS \citep{bolinLocalScaleInvariance2021}. These, however, may not have all of the desired properties of the CRPS and in particular cannot easily be transferred to a setting with predictive quantiles.

%In this paper we argue that these three aspects (evaluating the growth rate rather than absolute values, evaluating relative errors, giving more equal weights to all forecast targets) can all be addressed by simply applying the natural logarithm to forecasts (in our case predictive quantiles) and observations prior to computing the CRPS.

@@

For conceptual clarity and to allow for a more in-depth discussion, we focus mostly on the natural logarithm as a particular transformation (referred to as the log-transformtation in the remainder of this manuscript) in the context of epidemic phenomena. Instead of a score representing the magnitude of absolute errors, applying a log-transformation prior to the CRPS yields a score which a) measures relative error (see Section \ref{sec:methods:relative}), b) provides a measure for how well a forecast captures the exponential growth rate of the target quantity (see Section \ref{sec:methods:growthrate}) and c) is less dependent on the expected order of magnitude of the quantity to be predicted (see Section \ref{sec:methods:vst}). %The interpretation of the log-transformed score as a score for a forecast of the exponential growth rate of a given quantity aligns the evaluation with our understanding of how epidemiological processes should be modeled and the kinds of errors models would typically make. 
We therefore argue that such evaluations on the logarithmic scale should complement the prevailing evaluations on the natural scale. 
Other transformations may likewise be of interest. We briefly explore the square root transformation as an alternative transformation. %[and population standardization?]. 
Our analysis focuses on the CRPS (or WIS) as an evaluation metric, given its widespread use throughout the COVID-19 pandemic.

@@

If the mean-variance relationship is quadratic with $\sigma^2 = c \times \mu^2$, the natural logarithm can serve as the VST \citep{guerreroTimeseriesAnalysisSupported1993}. Denoting by $F^*$ the predictive distribution for $\log(Y)$, we can use the delta method to show that
$$
\mathbb{E}_F[\text{CRPS}\{F^*, \log(y)\}] \approx \frac{\sigma/\mu}{\sqrt{\pi}} 
= \frac{\sqrt{c}}{\sqrt{\pi}}
.
$$
The assumption of a quadratic mean-variance relationship is closely linked to the aspects discussed in Sections \ref{sec:methods:relative} and \ref{sec:methods:growthrate}. It implies that relative errors have constant variance and can thus be meaningfully compared across different targets. Also, it arises naturally if we assume that our capacity to predict the epidemic growth rate does not depend on the expected outcome.

If the variance is linear with $\sigma^2 = c \times \mu$, as with a Poisson-distributed variable, the square root is known to be a VST. Denoting by $\tilde{F}$ the predictive distribution for $\sqrt{Y}$, the delta method can again be used to show that
$$
\mathbb{E}_F[\text{CRPS}\{\tilde{F}, \sqrt{y}\}] \approx \frac{\sigma/\sqrt{\mu}}{2\sqrt{\pi}} = \frac{\sqrt{c}}{2\sqrt{\pi}}
.
$$

@@

In practice, one issue with transformations, such as the log transform, is that they are not readily applicable to negative numbers or zero values, which need to be removed or otherwise handled. Small discrete values can pose an additional problem as it may be difficult to reliably evaluate relative errors. 
One common approach is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm CITATION. This represents a strictly monotonic transformation and therefore preserves the propriety of the resulting score. The choice of the quantity to add does however influences scores and rankings, as measures of relative errors shrink when adding a constant to the forecast and the observation. The impact is greatest for forecasts of small quantities, as relative errors shrink more the smaller the original value before adding a constant. In principle, it would also be possible to exploit the difference in how scores are affected in order to equalise scores for forecasts of quantities across different scales by adding a larger number (e.g. 100 or 10,000) if average scores are dominated too strongly by forecasts for small quantities. 
%Add that the dispersion component can blow up

@@

Overall model rankings would be expected to differ even more when scores are averaged across multiple forecasts or targets. The change in rankings of aggregate scores is mainly driven by the order of magnitude of scores for different forecast targets across time, location and target type and less so by the kind of changes in model rankings for single forecasts discussed above. Large observations will dominate average CRPS values when evaluation is done on the natural scale, but much less so after log transformation. Depending on the relationship between the mean and variance of the forecast target, a log-transformation may even lead to systematically larger scores assigned to small forecast targets, as illustrated in Figure \ref{fig:SIM-wis-state-size-mean}. A different transformation like the square-root may then be more appropriate to make scores independent of the mean of the target quantity (as discussed in Section \ref{sec:methods:vst}).

@@

The log-transformation is only one of many transformations that may be useful and appropriate in an epidemiological context. One obvious option is to apply a population standardization to obtain incidence forecasts e.g., per 100,000 population If one is interested in multiplicative, rather than exponential growth rates, one could convert forecasts into forecasts for the multiplicative growth rate by dividing numbers by the last observed value. We suggested using the natural logarithm as a variance-stabilising transformation (VST) or alternatively the square-root transformation in the case of a Poisson distributed variable. Other VST like the Box-Cox \citep{boxAnalysisTransformations1964} are conceivable as well. Another promising transformation would be to take differences between forecasts on the log scale, or alternatively to divide each forecast by the forecast of the previous week (and analogously for observations), in order to obtain forecasts for week-to-week growth rates. One could then also ask forecasters to provide estimates of the weekly relative change applied to the latest data and subsequent forecast points directly. This would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory \citep[for a different approach to evaluating the shape of a forecast, see][]{srivastavaShapebasedEvaluationEpidemic2022}. This, unfortunately, is not feasible in the context of forecasts stored as predictive quantiles, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate, but may be an interesting approach if predictive samples are available as it enables the possibility of constructing composite scores as a weighted sum of scores based on different transformations. This would allow forecast consumers to assign explicit weights to different qualities of the forecasts they might care about.

@@

\begin{table}
\centering
\begin{tabular}{ccrrrrrr}
\toprule
Horizon & Target & $\alpha$ & $\beta$ & $\alpha_{\log}$ & $\beta_{\log}$ & $\alpha_{\sqrt{\ }}$ & $\beta_{\sqrt{\ }}$\\
\midrule
all & all & -1.093 & 0.963 & 0.390 & 0.001 & -0.995 & 0.209\\
\addlinespace
all & Cases & 0.036 & 0.858 & 0.751 & -0.033 & 0.047 & 0.201\\
all & Deaths & -0.885 & 0.868 & 0.430 & -0.021 & -7.564 & 0.826\\
\addlinespace
1 & all & -1.402 & 0.923 & 0.318 & -0.014 & 0.318 & 0.088\\
2 & all & -1.221 & 0.967 & 0.364 & -0.003 & 0.111 & 0.164\\
3 & all & -1.001 & 0.984 & 0.408 & 0.008 & -1.283 & 0.255\\
4 & all & -0.757 & 0.986 & 0.467 & 0.016 & -1.041 & 0.312\\
\addlinespace
1 & Cases & -0.861 & 0.876 & 0.433 & -0.024 & 0.785 & 0.087\\
2 & Cases & -0.243 & 0.877 & 0.660 & -0.031 & 0.959 & 0.162\\
3 & Cases & 0.372 & 0.855 & 0.882 & -0.037 & 1.115 & 0.238\\
4 & Cases & 0.816 & 0.837 & 1.009 & -0.036 & 1.665 & 0.296\\
\addlinespace
1 & Deaths & -1.145 & 0.831 & 0.376 & -0.035 & 0.458 & 0.048\\
2 & Deaths & -0.980 & 0.866 & 0.415 & -0.027 & 0.445 & 0.084\\
3 & Deaths & -0.809 & 0.885 & 0.441 & -0.016 & -8.262 & 0.903\\
4 & Deaths & -0.603 & 0.891 & 0.488 & -0.007 & -7.834 & 0.898\\
\bottomrule
\end{tabular}
\caption{Coefficients of three regressions for the effect of the magnitude of the median forecast on expected scores. The first regression was 
$\text{CRPS}(F, y) = \exp(\alpha) \cdot \text{median}(F)^{\beta},$ where $F$ is the predictive distribution and $y$ the observed value. The second one was 
$\text{CRPS}(\log F, \log y) = \alpha^* + \beta^* \cdot \log{(\text{median}(F))}.$ The third one was $\text{CRPS}(\sqrt{F}, \sqrt{y}) = \alpha^{**} + \beta^{**} \cdot \sqrt{(\text{median}(F))}.$
}
\label{tab:HUB-regression}
\end{table}

>>>>

\title{Transformation of forecasts for evaluating predictive performance in an epidemiological context}
  \author{Nikos I. Bosse\thanks{Department of Infectious Disease Epidemiology, London School of Hygiene \& Tropical Medicine, London, United Kingdom} $^{,}$\thanks{Centre for the Mathematical Modelling of Infectious Diseases, London, United Kingdom} $^{,*}$, 
  Sam Abbott\footnotemark[1] $^{,}$\footnotemark[2]$ ^{}$, 
  Anne Cori\thanks{MRC Centre for Outbreak Analysis and Modelling, Department of Infectious Disease Epidemiology, School of Public Health, Imperial College London, London, United Kingdom} $^{}$, \\
  Edwin van Leeuwen\thanks{Department of Infectious Disease Epidemiology, London School of Hygiene \& Tropical Medicine, London, United Kingdom} $^{,}$\thanks{UK Health Security Agency, London, United Kingdom} $^{}$, 
  Johannes Bracher\thanks{Chair of Statistical Methods and Econometrics, Karlsruhe Institute of Technology, Karlsruhe, Germany}$^{,}$\thanks{Computational Statistics Group, Heidelberg Institute for Theoretical Studies, Heidelberg, Germany} $^{}$, 
  Sebastian Funk\footnotemark[1] $^{,}$\footnotemark[2]$ ^{}$}

\maketitle
%\tableofcontents
\begin{abstract}
Forecast evaluation plays an essential role in the development cycle of predictive epidemic models and can inform their use for public health decision-making. Common scores to evaluate epidemiological forecasts are the Continuous Ranked Probability Score (CRPS) and the Weighted Interval Score (WIS), which are both measures of the absolute distance between the forecast distribution and the observation. They are commonly applied directly to predicted and observed incidence counts, but it can be questioned whether this yields the most meaningful results given the exponential nature of epidemic processes and the several orders of magnitude that observed values can span over space and time. In this paper, we argue that transforming counts before applying scores such as the CRPS or WIS can effectively mitigate these difficulties and yield epidemiologically meaningful and easily interpretable results. We motivate the procedure threefold using the CRPS on log-transformed counts as an example: firstly, it can be interpreted as a probabilistic version of a relative error. Secondly, it reflects how well models predicted the time-varying epidemic growth rate. And lastly, using arguments on variance-stabilizing transformations, it can be shown that under the assumption of a quadratic mean-variance relationship, the logarithmic transformation leads to expected CRPS values which are independent of the order of magnitude of the predicted quantity. Applying the log transformation to data and forecasts from the European COVID-19 Forecast Hub, we find that it changes model rankings regardless of stratification by forecast date, location or target types. Situations in which models missed beginning upward swings are more strongly emphasized while failing to predict a downturn following a peak is less severely penalized. We conclude that appropriate transformations, of which the natural logarithm is only one particularly attractive option, should be considered when assessing the performance of different models in the context of infectious disease incidence.

%Forecast evaluation plays an essential role in improving forecasting models and can support their role in informing decision-making. In epidemiology, probabilistic forecasts are often scored using the Weighted Interval Score (WIS) or the Continuous Ranked Probability Score (CRPS), which are measures of absolute distance between forecast and observation. Infectious disease transmission is commonly modelled as an exponential process characterized by the growth rate or the effective reproduction number. However, if the true objective of the forecaster is to predict future growth rates or reproduction numbers then scoring based on the absolute distance between forecast and observation may not reflect this underlying task well and thus make it difficult to compare forecasts across time, space, and forecast targets. As a solution, we propose transforming the data before scoring the forecasts to better reflect the underlying generative process. We further propose the natural logarithm  as a candidate transformation and discuss its interpretation as a measure of relative error and as a score for an implicit forecast of the exponential growth rate. Applying the natural logarithm to data from the European COVID-19 Forecast Hub, we found that it changed model rankings, regardless of stratification by forecast date, location or target types, and emphasised situations in which models missed lower inflection points and consequent rises in numbers, while penalising missed peaks less severely. We conclude that appropriate transformations, of which the natural logarithm is only one possible option, should be considered when assessing the performance of different models in the context of infectious disease incidence. 
\end{abstract}

@@

The dynamics of infectious processes are often described by the complementary concepts of the reproduction number $R$ \citep{gosticPracticalConsiderationsMeasuring2020} and growth rate $r$ \citep{wallingaHowGenerationIntervals2007}, where $R$ describes the strength and $r$ the speed of epidemic growth \citep{dushoffSpeedStrengthEpidemic2021}.
In the absence of changes in immunity, behaviour or other factors that may affect the intensity of transmission, the reproduction number would be expected to remain approximately constant.
In that case, the number of new infections in the population grows exponentially in time.
This behaviour was observed, for example, early in the COVID-19 pandemic in many countries~\citep{pellisChallengesControlCOVID192021}.

If case numbers are evolving based on an exponential process and the  modelling task revolves around estimating the reproduction number or the corresponding growth rate, then evaluating forecasts based on the absolute distance between forecast and observed value penalises underprediction (of the reproduction number or growth rate) less than overprediction by the same amount. This is because for exponential processes errors on the observed value grow exponentially with the error on the estimated reproduction number or growth rate. 
If one is to measure the ability of forecasts to assess and forecast the underlying infection dynamics, it may thus be more desirable to evaluate errors on the growth rate directly.

Evaluating forecasts using the CRPS or WIS means that scores represent a measure of absolute errors. However, forecast consumers may find errors on a relative scale easier to interpret and more useful in order to track predictive performance across targets of different orders of magnitude. 
\cite{bolinLocalScaleInvariance2021} have proposed the scaled CRPS (SCRPS) which is locally scale invariant; however, it does not correspond to a relative error measure and lacks a straightforward interpretation as available for the CRPS.

A closely related aspect to relative scores (as opposed to absolute scores) is that in the evaluation one may wish to give similar weight to all considered forecast targets. As the CRPS typically scales with the order of magnitude of the quantity to be predicted, this is not the case for the CRPS, which will typically assign higher scores to forecast targets with high expected values (e.g., in large locations or around the peak of an epidemic). \cite{bracherEvaluatingEpidemicForecasts2021} have argued that this is a desirable feature, directing attention to situations of particular public health relevance. An evaluation based on absolute errors, however, will assign little weight to other potentially important aspects, such as the ability to correctly predict future upswings while observed numbers are still low.

@@

For conceptual clarity and to allow for a more in-depth discussion, we focus mostly on the natural logarithm as a particular transformation (referred to as the log-transformtation in the remainder of this manuscript) in the context of epidemic phenomena. Instead of a score representing the magnitude of absolute errors, applying a log-transformation prior to the CRPS yields a score which a) measures relative error (see Section \ref{sec:methods:relative}), b) provides a measure for how well a forecast captures the exponential growth rate of the target quantity (see Section \ref{sec:methods:growthrate}) and c) is less dependent on the expected order of magnitude of the quantity to be predicted (see Section \ref{sec:methods:vst}). %The interpretation of the log-transformed score as a score for a forecast of the exponential growth rate of a given quantity aligns the evaluation with our understanding of how epidemiological processes should be modeled and the kinds of errors models would typically make. 
We therefore argue that such evaluations on the logarithmic scale should complement the prevailing evaluations on the natural scale. 
Other transformations may likewise be of interest. We briefly explore the square root transformation as an alternative transformation. %[and population standardization?]. 
Our analysis mostly focuses on the CRPS (or WIS) as an evaluation metric for probabilistic forecasts, given its widespread use throughout the COVID-19 pandemic.

@@

If the mean-variance relationship is quadratic with $\sigma^2 = c \times \mu^2$, the natural logarithm can serve as the VST \citep{guerreroTimeseriesAnalysisSupported1993}. Denoting by $F_{\log}$ the predictive distribution for $\log(Y)$, we can use the delta method to show that
$$
\mathbb{E}_F[\text{CRPS}\{F_{\log}, \log(y)\}] \approx \frac{\sigma/\mu}{\sqrt{\pi}} 
= \frac{\sqrt{c}}{\sqrt{\pi}}
.
$$
The assumption of a quadratic mean-variance relationship is closely linked to the aspects discussed in Sections \ref{sec:methods:relative} and \ref{sec:methods:growthrate}. It implies that relative errors have constant variance and can thus be meaningfully compared across different targets. Also, it arises naturally if we assume that our capacity to predict the epidemic growth rate does not depend on the expected outcome.

If the variance is linear with $\sigma^2 = c \times \mu$, as with a Poisson-distributed variable, the square root is known to be a VST. 
Denoting by $F_{\sqrt{\ }}$ the predictive distribution for $\sqrt{Y}$, the delta method can again be used to show that
$$
\mathbb{E}_F[\text{CRPS}\{F_{\sqrt{\ }}, \sqrt{y}\}] \approx \frac{\sigma/\sqrt{\mu}}{2\sqrt{\pi}} = \frac{\sqrt{c}}{2\sqrt{\pi}}
.
$$

@@

In practice, one issue with transformations, such as the log transform, is that they are not readily applicable to negative numbers or zero values, which need to be removed or otherwise handled. 
One common approach to deal with zeros is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm \citep{bellegoDealingLogsZeros2022}. This represents a strictly monotonic transformation and therefore preserves the propriety of the resulting score. The choice of the quantity to add does however influences scores and rankings, as measures of relative errors shrink when adding a constant to the forecast and the observation. The impact is greatest for forecasts of small quantities, as relative errors shrink more the smaller the original value before adding a constant. In principle, it would also be possible to exploit the difference in how scores are affected in order to equalise scores for forecasts of quantities across different scales by adding a larger number (e.g. 100 or 10,000) if average scores are dominated too strongly by forecasts for small quantities.

Small discrete observed values can pose an additional problem as it may be difficult to reliably evaluate relative errors. A related issues occurs when the predictive distribution has a large probability mass on zero (or on very small values), as this can translate into an excessively wide forecast in relative terms. This can be seen in Figure \ref{fig:HUB-model-comparison-baseline}, where the dispersion component of the WIS is inflated for scores obtained after applying the natural logarithm where forecasts contained zero in its prediction intervals.

@@

Overall model rankings would be expected to differ even more when scores are averaged across multiple forecasts or targets. The change in rankings of aggregate scores is mainly driven by the order of magnitude of scores for different forecast targets across time, location and target type and less so by the kind of changes in model rankings for single forecasts discussed above. Large observations will dominate average CRPS values when evaluation is done on the natural scale, but much less so after log transformation. Depending on the relationship between the mean and variance of the forecast target, a log-transformation may even lead to systematically larger scores assigned to small forecast targets, as illustrated in Figure \ref{fig:SIM-wis-state-size-mean}.

%A different transformation like the square-root may then be more appropriate to make scores independent of the mean of the target quantity (as discussed in Section \ref{sec:methods:vst}).

@@

The log-transformation is only one of many transformations that may be useful and appropriate in an epidemiological context. One obvious option is to apply a population standardization to obtain incidence forecasts e.g., per 100,000 population If one is interested in multiplicative, rather than exponential growth rates, one could convert forecasts into forecasts for the multiplicative growth rate by dividing numbers by the last observed value. We suggested using the natural logarithm as a variance-stabilising transformation (VST) or alternatively the square-root transformation in the case of a Poisson distributed variable. Other VST like the Box-Cox \citep{boxAnalysisTransformations1964} are conceivable as well. Another promising transformation would be to take differences between forecasts on the log scale, or alternatively to divide each forecast by the forecast of the previous week (and analogously for observations), in order to obtain forecasts for week-to-week growth rates. One could then also ask forecasters to provide estimates of the weekly relative change applied to the latest data and subsequent forecast points directly. This would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory \citep[for a different approach to evaluating the shape of a forecast, see][]{srivastavaShapebasedEvaluationEpidemic2022}. This, unfortunately, is not feasible for forecasts stored as predictive quantiles, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate, but may be an interesting approach if predictive samples are available. It is possible to go beyond choosing a single transformation by constructing composite scores as a weighted sum of scores based on different transformations. This would make it possible to create custom scores and allow forecast consumers to assign explicit weights to different qualities of the forecasts they might care about.

@@

\begin{table}
\centering
\begin{tabular}{ccrrrrrr}
\toprule
Horizon & Target & $\alpha$ & $\beta$ & $\alpha_{\log}$ & $\beta_{\log}$ & $\alpha_{\sqrt{\ }}$ & $\beta_{\sqrt{\ }}$\\
\midrule
all & all & -1.093 & 0.963 & 0.390 & 0.001 & -0.995 & 0.209\\
\addlinespace
all & Cases & 0.036 & 0.858 & 0.751 & -0.033 & 0.047 & 0.201\\
all & Deaths & -0.885 & 0.868 & 0.430 & -0.021 & -7.564 & 0.826\\
\addlinespace
1 & all & -1.402 & 0.923 & 0.318 & -0.014 & 0.318 & 0.088\\
2 & all & -1.221 & 0.967 & 0.364 & -0.003 & 0.111 & 0.164\\
3 & all & -1.001 & 0.984 & 0.408 & 0.008 & -1.283 & 0.255\\
4 & all & -0.757 & 0.986 & 0.467 & 0.016 & -1.041 & 0.312\\
\addlinespace
1 & Cases & -0.861 & 0.876 & 0.433 & -0.024 & 0.785 & 0.087\\
2 & Cases & -0.243 & 0.877 & 0.660 & -0.031 & 0.959 & 0.162\\
3 & Cases & 0.372 & 0.855 & 0.882 & -0.037 & 1.115 & 0.238\\
4 & Cases & 0.816 & 0.837 & 1.009 & -0.036 & 1.665 & 0.296\\
\addlinespace
1 & Deaths & -1.145 & 0.831 & 0.376 & -0.035 & 0.458 & 0.048\\
2 & Deaths & -0.980 & 0.866 & 0.415 & -0.027 & 0.445 & 0.084\\
3 & Deaths & -0.809 & 0.885 & 0.441 & -0.016 & -8.262 & 0.903\\
4 & Deaths & -0.603 & 0.891 & 0.488 & -0.007 & -7.834 & 0.898\\
\bottomrule
\end{tabular}
\caption{Coefficients of three regressions for the effect of the magnitude of the median forecast on expected scores. The first regression was 
$\log[\text{CRPS}(F, y)] = \alpha + \beta \times \log[\text{median}(F)], $ where $F$ is the predictive distribution and $y$ the observed value. The second one was 
$\text{CRPS}(F_{\log}, \log y) = \alpha_{\log} + \beta_{\log} \cdot \log{(\text{median}(F))},$ where $F_{\log}$ is the predictive distribution for $\log y$. The third one was $\text{CRPS}(F_{\sqrt{\ }}, \sqrt{y}) = \alpha_{sqrt{\ }} + \beta_{sqrt{\ }} \cdot \sqrt{(\text{median}(F))},$ where $F_{\sqrt{\ }}$ is the predictive distribution for $\sqrt{y}$.
}
\label{tab:HUB-regression}
\end{table}
